Unreliable heterogeneity: how measurement error obscures heterogeneity in meta-analyses in psychology

### 2023-06-17 manuscript/manuscript.qmd
updated flowchart to include hs

```{r Figure 1, out.width= "85%"}
#| fig.env: figure*
#| fig-pos: 't'
#| fig-cap: "Figure 1. Flowchart summarizing the simulation design. The flowchart shows the procedures followed to meta-anlyze results using the Hedge’s and Vevea model (see ‘Meta-Analytic Model’ header in methods section). The Hunter & Schmidt ‘bare-bones’ meta-analytic model followed the Pearson correlations procedure, but used sample size weights and replaced $r_i$ in the sampling variance by $\\bar{r}$ for meta-anlysis."

>>>>

```{r Figure 1, out.width= "85%"}
#| fig.env: figure*
#| fig-pos: 't'
#| fig-cap: "Figure 1. Flowchart summarizing the simulation design."
